% Reference CV, hand-written LaTeX baseline for the docgen comparison bench.
% Compiles standalone with Tectonic (XeTeX engine). One A4 page, no assets.
\documentclass[10pt]{article}
\usepackage[a4paper,margin=1.3cm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}

\definecolor{accent}{HTML}{0F62FE}
\definecolor{dim}{HTML}{5A5A5A}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

\titleformat{\section}{\normalsize\bfseries\color{accent}}{}{0pt}{\MakeUppercase}[\vspace{-7pt}{\color{accent!50}\rule{\textwidth}{0.6pt}}]
\titlespacing*{\section}{0pt}{9pt}{4pt}

\newcommand{\entry}[3]{\textbf{#1} \textperiodcentered{} #2 \hfill {\color{dim}\small #3}\par}

\setlist[itemize]{leftmargin=1.1em,itemsep=1pt,topsep=2pt,parsep=0pt,label=\textcolor{accent}{\textbullet}}

\begin{document}

{\LARGE\bfseries Alex Martin}\par\vspace{1pt}
{\color{accent}\bfseries Machine Learning Engineer — LLM Systems \& MLOps}\par\vspace{1pt}
{\small\color{dim} alex.martin@example.com \textperiodcentered{} +33 6 12 34 56 78 \textperiodcentered{} Paris, France \textperiodcentered{} linkedin.com/in/alex-martin-ml \textperiodcentered{} github.com/alexmartin-ml \textperiodcentered{} alexmartin.dev}

\section{Summary}
ML engineer with 4 years of experience taking LLM and computer-vision systems from prototype to production. Designed RAG platforms serving 40k daily queries, cut inference costs by 35\%, and led the MLOps practice for a 12-person data team. Looking to build AI products that survive contact with real users.

\section{Experience}
\entry{Machine Learning Engineer}{Lumina AI}{Paris, France \textperiodcentered{} Jan 2024 -- Present}
\begin{itemize}
  \item Architected the retrieval-augmented generation platform behind the flagship assistant: hybrid BM25 + dense retrieval, reranking, and grounded citation checks serving 40k queries/day at p95 \textless{} 900 ms.
  \item Cut LLM serving costs 35\% by routing between fine-tuned small models and frontier APIs based on query complexity scoring.
  \item Built the evaluation harness (LLM-as-judge + golden sets) that gates every prompt and model change in CI.
\end{itemize}
\vspace{3pt}
\entry{Data Scientist}{Nexa Retail Group}{Lille, France \textperiodcentered{} Sep 2021 -- Dec 2023}
\begin{itemize}
  \item Shipped demand-forecasting models (gradient boosting, hierarchical reconciliation) covering 1,200 stores, reducing stockouts 18\%.
  \item Industrialized the feature pipeline on Spark + Airflow; training-to-deploy time fell from 3 weeks to 2 days.
  \item Mentored two junior data scientists and ran the team's paper-reading group.
\end{itemize}
\vspace{3pt}
\entry{Research Intern — Computer Vision}{INRIA}{Grenoble, France \textperiodcentered{} Feb 2021 -- Aug 2021}
\begin{itemize}
  \item Implemented self-supervised pretraining (SimCLR variants) for defect detection on industrial imagery; +9 mAP over the supervised baseline with 10x less labeled data.
\end{itemize}

\section{Education}
\entry{MSc Computer Science — Machine Learning}{Université Grenoble Alpes}{Grenoble \textperiodcentered{} 2019 -- 2021}
\begin{itemize}
  \item Thesis: contrastive pretraining for industrial vision. Graduated with highest honors.
\end{itemize}
\vspace{3pt}
\entry{BSc Mathematics \& Computer Science}{Université de Lille}{Lille \textperiodcentered{} 2016 -- 2019}

\section{Skills}
\textbf{ML \& LLM:} PyTorch, RAG, fine-tuning (LoRA), evaluation, vLLM, embeddings\par
\textbf{Data \& Infra:} Python, SQL, Spark, Airflow, Kafka, Postgres\par
\textbf{MLOps \& Cloud:} Docker, Kubernetes, GCP (Vertex, Cloud Run), CI/CD, monitoring \& drift

\section{Projects}
\textbf{OpenRecruit} \textperiodcentered{} FastAPI, React, Typst \hfill\par
Open-source CV tailoring tool: structured generation with schema-enforced LLM output and millisecond document rendering.\par\vspace{2pt}
\textbf{GPU cost dashboard} \textperiodcentered{} Grafana, Prometheus\par
Real-time per-team GPU utilization and cost attribution adopted by 3 squads.

\section{Languages \& Certifications}
\textbf{Languages:} French (native), English (C1), Spanish (B1)\par
\textbf{Certifications:} GCP Professional ML Engineer, Google Cloud, 2024\par
\textbf{Interests:} Trail running, Chess (1800 ELO), Synthesizers

\end{document}
